% Real-bug detection subsection.

\subsection{Real-Bug Detection}
\label{sec:bug-bench}

\input{sections/bug_bench_table.tex}

\paragraph{Setup and manifest construction.}
We complement \S\ref{sec:mutation-adequacy} with a real-bug
benchmark in the
Magma~\citep{hazimeh2020magma}\,/\,FuzzBench~\citep{metzman2021fuzzbench}
ground-truth style. The manifest is $32$ historical parser bugs
($23$ VCF $+ 9$ SAM), each pinned to a verified
$V_{\mathrm{pre}}{\to}V_{\mathrm{post}}$ commit pair. Candidates
are sourced from each SUT's upstream release notes and
\texttt{bug}-label PRs over the last five years (we do not mine
\texttt{git log} for suspicious commits). A candidate enters iff
all four hold: (i) reachable through the file-input pipeline as a
parse exception, canonical-JSON value diff, or write-roundtrip
diff; (ii) pre-fix and post-fix observably differ on the same
input; (iii) the anchor pair reproduces empirically; (iv) both
versions install as a pinned artefact. Failures are transparently
dropped per standard ground-truth bench
protocol~\cite{hazimeh2020magma}, with the drop log in the
artefact. Each entry ships a minimum-shape text PoV authored by
reading the fix's \texttt{---/+++} diff.

\paragraph{Detection predicate, tool slate, and budget.}
Detection follows a pre-fix\,/\,post-fix differential predicate
in the ground-truth fuzzing style of
Magma~\cite{hazimeh2020magma}: tool $T$ detects bug $B$ iff some
input $I$ that $T$'s adapter produced during the budget satisfies
$\mathit{signal}_T(I, V_{\mathrm{pre}}) \neq
\mathit{signal}_T(I, V_{\mathrm{post}})$. The slate runs eight
tools: the five coverage-guided fuzzers of
\S\ref{sec:mutation-adequacy}, \biotest{}, an uninformed
Pure-Random floor~\citep{klees2018fuzz}, and two unit-level Java
baselines (EvoSuite~\citep{fraser2011evosuite} under an
``EvoSuite-anchor'' protocol that generates a JUnit suite against
$V_{\mathrm{post}}$ and replays against $V_{\mathrm{pre}}$, plus
Randoop~\citep{pacheco2007randoop}). Per Magma-style
methodology~\citep{hazimeh2020magma}, every input fuzzer's seed
corpus includes the manifest's canonical PoV alongside Tier-1+2
spec-example seeds, equalising starting positions. The per-bug
budget is $7200$\,s, gated by a language-eligibility matrix.

\paragraph{Headline.}
Table~\ref{tab:bugbench-headline} reports per-(SUT, format)
detection counts. \biotest{} detects $10/32$ (htsjdk/VCF $4$,
htsjdk/SAM $2$, vcfpy/VCF $3$, noodles/VCF $1$), every other
input fuzzer detects $0/32$, and the any-tool union with the
unit-level Java baselines is $14/32$. Forward (pre-fix rejects,
post-fix accepts) fires on eight \emph{over-strict} regressions
spanning htsjdk stringency edge-cases, vcfpy lazy-evaluation
traps, and a noodles writer round-trip. Reverse (pre-fix wrongly
accepts, post-fix rejects) fires on two htsjdk
\emph{accept-when-should-reject} regressions where the buggy
version silently mis-classified or mis-counted a record.
Crash-only oracles surface neither shape without a deliberate
exception~\citep{klees2018fuzz}, which is why the crash-only
slate scores $0$ on every (SUT, format) row.

\paragraph{Why the unit-level baselines reach four htsjdk bugs
the input fuzzers do not.}
EvoSuite~\citep{fraser2011evosuite} synthesises JUnit cases by
genetic search over method-call sequences, and
Randoop~\citep{pacheco2007randoop} constructs feedback-directed
random sequences over the same surface. Both bypass file parsing
entirely by constructing \texttt{VariantContext} /
\texttt{SAMRecord} instances via the API. Of the four manifest
entries reached this way and not by the input-fuzzing slate, one
is a \texttt{VariantContextBuilder} regression structurally
out-of-scope for any file-input fuzzer, and the other three are
parse-time-reachable in principle but \biotest{}'s spec-grounded
MR transforms in the per-cell budget did not synthesise a trigger
that isolated the patch from co-occurring spec violations.

\paragraph{Why \biotest{} leads in absolute count.}
Despite seeing the SUT only through file parse + round-trip,
\biotest{} is above both unit-level baselines on absolute count
($10>4>3$). Two effects dominate. First, \biotest{} applies to
all four host languages while EvoSuite and Randoop are Java-only
and run on the htsjdk row alone ($12$ of $32$ cells). On that
shared subset \biotest{} still leads ($6/12$ vs $4/12$ vs
$3/12$). Second, the differential and metamorphic oracles surface
silent value-disagreement bugs (e.g.\ mis-counted AC/AN/AF) that
neither crash-only fuzzers nor unit-level GA can detect without
an external comparator: crash-only oracles by
construction~\citep{klees2018fuzz}, and unit-level GA because its
assertions are derived from a single SUT version's observed
output.
