% Code-coverage subsection.

\subsection{Code Coverage}
\label{sec:coverage}

\paragraph{Setup.}
We complement mutation-adequacy with a code-coverage measurement
on the same six $(\mathrm{SUT, format})$ pairs, scoped by the same
target-class filter the mutation engine uses
(\S\ref{sec:design-fairness}) so the two metrics are graded on the
same SUT surface. Line coverage (the fraction of source lines in
each parser executed at least once during a tool's campaign) is
collected by each language's standard coverage instrumentation
(specific backends are listed in \S\ref{sec:implementation}). We
report final-attainment line coverage, the end-of-campaign value
each tool reaches inside its scope, because \biotest's Phase-D
feedback loop (Figure~\ref{fig:pipeline}) terminates on its own
stop-criteria rather than at a fixed wall-clock tick. Within each
row of Table~\ref{tab:coverage-headline} the scope filter and
instrumentation backend are identical across columns. Line
percentages are directly comparable as final attainment.

\input{sections/coverage_table.tex}

\paragraph{Headline observations and take-away.}
On the three VCF SUTs \biotest{} attains the highest mean final
line coverage of any tool we measured ($44.75{\pm}1.61$\% on
htsjdk, $74.12{\pm}1.52$\% on vcfpy, $36.15{\pm}1.43$\% on
noodles). On SAM \biotest{} trails the strongest baseline on
each parser: by $4.20$\,pp on htsjdk ($20.85$\% vs Jazzer's
$25.05$\%), by $5.75$\,pp on biopython ($48.65$\% vs Atheris's
$54.40$\%), and by $7.10$\,pp on seqan3 ($91.35$\% vs
libFuzzer's $98.45$\%).
The pattern is consistent with the mutation-adequacy result of
\S\ref{sec:mutation-adequacy}, and the VCF/SAM asymmetry has a
concrete structural explanation. VCF depends on declarative
typing constraints in the header (\texttt{INFO}, \texttt{FORMAT},
contig declarations) that constrain record-level parsing, and
\biotest{}'s spec-grounded generator exercises these constraints
preferentially because each is named in the spec and retrieved by
LLM mining. SAM depends more on flag-bit combinations and
CIGAR-shape diversity within record bodies, where coverage-guided
byte mutators accumulate inputs reaching rare control-flow paths
more efficiently than spec-driven enumeration. The same asymmetry
surfaces on the mutation-adequacy
axis~\cite{klees2018fuzz,boehme2020boosting}.
