% Design section for the BioTest paper.

\section{Design}
\label{sec:design}

\biotest{} treats a parser as an opaque function from bytes to a
structured record set and exercises it via spec-derived metamorphic
relations~\citep{chen1998metamorphic,chen2018metamorphic,segura2016survey},
multi-runner consensus oracles, and coverage-steered corpus
augmentation. The framework remains useful across heterogeneous
parser implementations of the same format without per-SUT
engineering effort beyond the parse-and-emit shim that
coverage-guided fuzzers already require. VCF~\citep{danecek2011vcf}
and SAM~\citep{li2009sam} are partially context-sensitive textual
formats: header declarations constrain record-level types, and
they admit multiple semantically-equivalent surface forms (tag
order, integer encodings, mandatory-vs-default values) that make
them amenable to metamorphic testing.

\subsection{Design Constraints}
\label{sec:design-constraints}

\biotest{} is built on three constraints. \textbf{C1:
SUT-agnostic core.} The framework contains no per-SUT logic in
any phase. \textbf{C2: Per-SUT user effort bounded by what
coverage-guided fuzzers already require.} Onboarding a parser is
a thin \emph{harness} that calls the parser and emits a
canonical-JSON record set, plus a $\sim$50-line Python
\emph{runner} subclass that wraps the harness for the
orchestrator. The harness conforms to a fixed per-format
canonical schema (typed fields, deterministic ordering, 1-based
coordinates). \biotest{} adds \emph{no other per-SUT artefact}: no
metamorphic relation, oracle predicate, seed corpus, instrumented
build, bytecode-rewriting agent, or fork-server harness.
\textbf{C3: Semantic-digest oracle.} A violation is declared when
the observable parse outcome (parse-success flag, canonical-JSON
digest, exception class) diverges, with no per-SUT assertion
code. The oracle's intermediate strength forfeits
coverage-feedback's bug-finding advantage on byte-content-lenient
parsers~\citep{klees2018fuzz,boehme2020boosting} in exchange for
portability across four parser languages.

\subsection{Pipeline}
\label{sec:design-pipeline}

The framework runs as five phases (Figure~\ref{fig:pipeline}).
Phases~A and~B run once per format, and phases~C, D, and~E run
per iteration on the SUT pool. \textbf{Phase~A} chunks the
published specification and embeds the chunks into a vector store
for retrieval-augmented prompting~\citep{lewis2020rag}, parametric
over format and spec version. \textbf{Phase~B} prompts an LLM to
propose candidate metamorphic relations
$\mathit{out}(\mathit{parse}(x)) \equiv
\mathit{out}(\mathit{parse}(T(x)))$, each grounded in spec rules
retrieved from the Phase~A store and validated against a reference
parser on a seed corpus before admission. \textbf{Phase~C} routes
each input $x$ and its transform $T(x)$ through every configured
parser runner. Outputs are canonicalised to JSON and graded by the
consensus oracle of \S\ref{sec:design-consensus}, which layers
metamorphic equivalence on top of differential
agreement~\citep{mckeeman1998differential}. \textbf{Phase~D}
reduces coverage telemetry to per-class blind-spot tickets and
folds the highest-yield uncovered classes back into Phase~B's
prompt. \textbf{Phase~E} content-hashes inputs accepted by at
least one runner and runs the augmentation operators of
\S\ref{sec:design-corpus} (Ranks~8--13).

\input{sections/pipeline_figure}

\subsection{Corpus Stack}
\label{sec:design-corpus}

A pure metamorphic test loop ceilings at modest line coverage on
file-format parsers. We therefore widen the corpus along two tiers
ordered by decreasing semantic preservation. Ranks~1--7 are
semantics-preserving metamorphic transforms whose outputs the
consensus oracle scores under the metamorphic predicate.
Ranks~8--13 trade strict semantic equivalence for branch and value
diversity, and their outputs feed mutation grading and the
differential-only oracle, which does not require metamorphic
validity to declare a kill.

\begin{itemize}\setlength{\itemsep}{1pt}
  \item \textbf{Ranks~1--7 (metamorphic).} LLM-synthesised seeds
  (R1), upstream-derived corpora (R2), spec-rule-targeted
  malformed mutators (R3), Hypothesis-targeted property-based
  generation (R4), API-query relations
  $P(\mathit{parse}(x))\equiv P(\mathit{parse}(T(x)))$ over
  reflection-discovered scalar getters (R5), opt-in
  LLM-synthesised relations (R6), and theme-restricted
  spec-invariant registries (R7).

  \item \textbf{R8 corpus keeper.} Persists every transformed
  input accepted by at least one runner, deduplicated by canonical
  AST-hash.

  \item \textbf{R9 value diversifier.} Perturbs spec-bounded
  numerical fields (POS, QUAL, MAPQ, AF, DP, TLEN) within bounds,
  gated by a canonical-normaliser validity check.

  \item \textbf{R10 byte fuzzer.} Validity-gated bit-flip,
  byte-substitution, byte-insert, and byte-delete operators on
  non-header positions.

  \item \textbf{R11 boundary-value generator.} Boundary Value
  Analysis~\citep{myers1979art} on spec-bounded numerical fields.

  \item \textbf{R12 structural variant generator.} Spec-derived
  enumerator emitting branch-diverse inputs (CIGAR-shape mixes,
  tag-type permutations, multi-sample records, varied
  FILTER/INFO/FORMAT compositions).

  \item \textbf{R13 lenient byte fuzzer.} Weak-gate byte-level
  mutator retaining files with at least one line. Not metamorphic,
  consumed only by mutation-adequacy grading.
\end{itemize}

\subsection{Consensus Oracle}
\label{sec:design-consensus}

Phase~C parses each input with $N \ge 3$ SUTs drawn from the
runner pool. The VCF pool is htsjdk, vcfpy, noodles, and pysam.
The SAM pool is htsjdk, biopython, seqan3, and pysam. When the
SUT under grading is one of these runners, the remaining three
voters supply the consensus.
Each runner emits a parsed record set canonicalised to JSON and
hashed, alongside an exception class on failure. The oracle
classifies the input under three layered predicates. (i)
Differential consensus: if a strict majority of runners agrees on
a digest $\sigma^\star$ and runner $i$ disagrees, runner~$i$ is
implicated. (ii) Metamorphic consensus: if
$\sigma^\star_x = \sigma^\star_{T(x)}$ but
$\sigma_i^x \ne \sigma_i^{T(x)}$, runner~$i$ is implicated. (iii)
Relation quarantine: if the consensus disagrees on $x$ versus
$T(x)$, the relation has misclassified what the spec says is
semantics-preserving. The choice $N\ge 3$ is the minimum that
admits a strict majority and distinguishes ``one runner is wrong''
from ``the spec is
ambiguous''~\citep{barr2015oracle}.

\subsection{Cross-Tool Fairness Recipe}
\label{sec:design-fairness}

\S\ref{sec:evaluation} grades \biotest{} against coverage-guided
fuzzers under four identical conditions. Each pair uses the same
mutation engine (PIT~\citep{coles2016pit} for htsjdk,
mutmut~\citep{mutmut2024} for vcfpy and biopython,
cargo-mutants~\citep{cargomutants2024} for noodles, a DIY
mull-style \textsc{aor}/\textsc{ror}/\textsc{lor} operator
set~\citep{denisov2018mull,just2014mutants} for seqan3), the same
target-class scope, the same kill predicate (parse-success flip,
canonical-JSON divergence, or crash-class flip) scored as
$\mathit{killed}/\mathit{reachable}$~\citep{coles2016pit,papadakis2019mutation},
and the same wall-clock budget per pair across $n$ reps. Only the
corpus differs.

Wall-clock parity is not iteration-cost parity. In-process fuzzers
iterate faster than fork-server fuzzers, and the imbalance shows
up on seqan3/SAM as a $17$\,pp gap between
AFL++~\citep{fioraldi2020aflpp} and
libFuzzer~\citep{libfuzzer2024} despite identical mutants. Every corpus is trimmed to $\le 200$
files by an AFL-cmin-style minimiser using per-file
kill-cardinality on Python SUTs~\citep{vikram2023guiding} and an
SUT-agnostic outcome-fingerprint elsewhere. The selector adds
$+1$ to $+2$\,pp on pairs where it actively trims. As an
uninformed-fuzzing reference~\citep{klees2018fuzz} we add a
Pure-Random byte emitter under identical conditions and report it
as a per-pair floor.
