\section{Implementation}
\label{sec:implementation}

\biotest{} is a Python orchestrator. Per-language SUT runners
delegate parser invocation to the SUT's native toolchain, and the
five phases of \S\ref{sec:design} are realised concretely as
follows.

\paragraph{Specification ingest (Phase~A).}
The published format specification is segmented at rule and
field-definition boundaries, embedded with a sentence-transformer
encoder, and indexed in a ChromaDB vector store. The same store
serves every SUT for the format and is rebuilt only when the spec
version changes.

\paragraph{LLM mining (Phase~B).}
The runs reported here use \texttt{deepseek-v4-flash} via the
DeepSeek API. The orchestrator is provider-agnostic. The prompt
retrieves the top-ranked spec chunks by cosine similarity to the
rule the proposal must cite~\citep{lewis2020rag} and constrains
the model to a whitelist of $\sim 20$ atomic transforms registered
in the framework. Each candidate MR traverses three sequential
gates. The whitelist gate rejects unrecognised transforms. The
hash gate collapses candidates whose
$(\mathit{format}, \mathit{scope}, \mathit{transform\_steps})$
tuple matches an already-admitted MR, so LLM nondeterminism does
not inflate the registry. The seed-corpus gate validates the
round-trip equality on a hand-curated reference corpus before
admission, and is the load-bearing rejection cause across recorded
snapshots. The first targeted mining run on the
\texttt{ordering\_invariance} intent for VCF admitted three
enforced MRs out of seven candidate themes, and the per-pair
enforced count in the headline runs ranges from $3$ for SAM to
$10$ for VCF. Figure~\ref{fig:llm-io} traces the pipeline through
one such accepted MR with real artefacts from the spec chunk to
the validation outcome.

\input{sections/llm_io_figure}

\paragraph{Runner architecture (Phases~C, D).}
The runner subprocesses the SUT's harness, parses the
canonical-JSON digest, and exposes the result through a uniform
interface. Java harnesses run on a per-test JVM, Python harnesses
import the parser directly, Rust harnesses run via
\texttt{cargo test} against a generated crate, and C++ harnesses
are compiled once as a gcov-instrumented binary. Coverage is
collected with JaCoCo for Java, \texttt{coverage.py} for Python,
\texttt{cargo-llvm-cov} for Rust, and \texttt{gcovr} for C++.

\paragraph{Augmenters (Phase~E).}
Rank~12 and Rank~13 ship as stand-alone generators that are not
LLM-mined. Rank~12 outputs feed both the metamorphic oracle and
mutation grading. Rank~13 outputs feed only the latter, since
Rank~13 is intentionally not metamorphic.

\paragraph{Reproducibility.}
The orchestrator, SUT source pins, mutation engines, coverage
tools, and baseline fuzzers ship as a single Docker image on
Ubuntu~22.04. The C++ mutation engine is a re-implemented
default-operator set rather than upstream
Mull~\citep{denisov2018mull} due to a glibc/Ubuntu version
conflict. The artefact is deposited as an anonymised Zenodo
record (DOI placeholder for double-blind review, de-anonymised at
camera-ready) containing the Docker image digest, the source-tree
snapshot, the MR-curation log, and the per-pair raw kill counts
and bug-bench records. We commit to the venue's
artefact-evaluation track.
