% Mutation-adequacy subsection.

\subsection{Mutation Adequacy}
\label{sec:mutation-adequacy}

\paragraph{Setup.}
We grade the corpus produced by \biotest{} under the fairness
recipe of \S\ref{sec:design-fairness}. Six $(\mathrm{SUT,
format})$ pairs span four parser languages and four mutation
engines (htsjdk/VCF and htsjdk/SAM use PIT, vcfpy/VCF and
biopython/SAM use mutmut, noodles/VCF uses cargo-mutants, seqan3/SAM
uses a DIY mull-style operator set). The four close-margin pairs
(htsjdk/VCF, htsjdk/SAM, vcfpy/VCF, noodles/VCF) run at $n{=}10$
reps on the \biotest{} side after a power-driven boost from
$n{=}4$, with achieved baseline $n$ of $10/6/9/6$ respectively.
Biopython and seqan3 retain $n{=}4$ where samples are
deterministic ($\sigma{=}0.00$) or operate at the protocol's
budget-termination point. We report mean $\pm$ sample std,
with per-cell sample std (\biotest/baseline)
$0.71/1.34$, $0.28/1.83$, $0.11/1.91$, $1.42/1.21$, $0.79/0.36$,
$0.00/0.00$ for htsjdk/VCF, vcfpy/VCF, noodles/VCF, htsjdk/SAM,
biopython/SAM, seqan3/SAM. For biopython, the Atheris baseline
terminates at the 262\textsuperscript{nd} of 523 generated mutants
under shuffle seed 42, and we cap \biotest{} at the same 262
mutants for protocol parity, additionally reporting the
full-population result ($25.81{\pm}0.00\%$).

\input{sections/mutation_radar_figure.tex}

\paragraph{Significance testing.}
On the four close-margin pairs we use $n_{\mathrm{BT}}{=}10$ and
the achieved baseline $n$ shown in
Figure~\ref{fig:mutation-radar}. We compute exact two-sided
Mann--Whitney $U$ by full enumeration of the
$\binom{n_1+n_2}{n_1}$ rank arrangements (no normal
approximation), Vargha--Delaney
$\hat{A}_{12}$~\citep{vargha2000critique}, a non-parametric
effect size equal to the probability that a randomly drawn
\biotest{} sample exceeds a randomly drawn baseline sample
($0.5$ indicates no effect, values approaching $0$ indicate
\biotest{} is consistently below, and values approaching $1$
indicate \biotest{} is consistently above), with conventional
small/medium/large thresholds at $0.56/0.64/0.71$, and
Holm--Bonferroni correction at $k{=}4$. Three of four pairs
(htsjdk/VCF, htsjdk/SAM, noodles/VCF) clear family-wise
$\alpha{=}0.05$, with the strongest signal at htsjdk/VCF
(Holm $p{=}4.0\times 10^{-5}$). On vcfpy/VCF the gap to Atheris
under the new $n{=}10$ draw is $-0.05$\,pp
($87.32$ vs.\ $87.37$\,pp, $\hat{A}_{12}{\approx}0.5$): the
rep-distributions overlap and the cell reduces to a statistical
tie rather than a measurable deficit~\citep{arcuri2014statistical}.
For the three remaining close-margin pairs the descriptive ranking
(\biotest{} below the strongest baseline on the dominant majority
of rep-pairings) is an inferential conclusion at family-wise
$\alpha{=}0.05$, not a small-sample observation.

\paragraph{Biopython is where coverage-guided fuzzing genuinely wins.}
The visible $-32.5$\,pp dip on the biopython axis of
Figure~\ref{fig:mutation-radar} is the largest single signal in
the radar. It is measured under the matched-budget protocol that
caps both \biotest{} and Atheris at the first $262$ generated
mutants. Biopython's parser applies a strict structural validator
but accepts byte-level variation within field values, and Atheris
accumulates files that pass the validator and trip rare error
paths. Enabling our Rank-12 structural and Rank-13
lenient-byte-fuzz augmentation does not move the mean
($25.48{\pm}0.79$ vs.\ un-augmented $25.57{\pm}0.00$,
$\hat{A}_{12}{=}0.50$). This is the empirical pattern Klees et
al.\ and B\"ohme et al.~\cite{klees2018fuzz,boehme2020boosting}
report on byte-content-lenient parsers. Closing the gap requires
per-SUT bytecode instrumentation, outside our C2 envelope.

\paragraph{Three close-margin deficits, one statistical tie.}
On htsjdk/VCF, htsjdk/SAM, and noodles/VCF the \biotest{} vertex
and the strongest-baseline marker overlap visibly in
Figure~\ref{fig:mutation-radar}: the deficit ranges from
$-0.35$\,pp on noodles, through $-2.47$\,pp on htsjdk/SAM, to
$-4.19$\,pp on htsjdk/VCF. \biotest{} is below the baseline on
the dominant majority of
$n_{\mathrm{BT}}{\times}n_{\mathrm{base}}$ rep-pairings
($\hat{A}_{12} \in \{0.000, 0.111, 0.183\}$, all in the ``large''
magnitude band). On vcfpy/VCF the new $n{=}10$ draw produces
$87.32{\pm}0.28$\,pp against Atheris's $87.37{\pm}1.83$\,pp: a
$-0.05$\,pp difference inside both samples' standard deviations,
with absolute kills $815.7{\pm}6.3$ of $934.1{\pm}5.7$ reachable
for \biotest{} versus $832.0{\pm}30.6$ of $952.4{\pm}50.5$ for
Atheris. The rep-distributions overlap and we therefore claim
parity with Atheris on vcfpy/VCF rather than a deficit. We do not
claim ``match'' on the three remaining cells: Klees et
al.~\cite{klees2018fuzz} report a $2$--$5{\times}$ advantage for
coverage-guided fuzzers, and we measure how close grammar-driven
generation can come under our design constraints.

\paragraph{seqan3: the consensus oracle's retained corpus matters.}
The starred vertex on the radar marks the only axis where
\biotest{} exceeds every baseline outright: on seqan3/SAM
\biotest{} is $+6.87$\,pp above libFuzzer~\citep{libfuzzer2024} on
the means, with both samples deterministic ($\sigma{=}0.00$) under
repeated runs against the same corpus. We report only the mean
difference and decline to attach an $\hat{A}_{12}$ value, which on
a pair of scalar means is uninformative beyond the sign. The
mechanism is a corpus-retention difference under identical
engine-side kill semantics. \biotest's spec-driven generator
constructs inputs reaching distinct typed-exception classes
(CIGAR-shape, tag-type, and flag-bit boundaries via Rank~12),
whereas libFuzzer's coverage-guided byte mutator preferentially
retains crashes and discards inputs that merely produce a typed
exception. Mutations flipping one typed-exception class to another
register as kills only when the corpus contains an input reaching
the original class~\citep{barr2015oracle}.

Construct- and internal-validity threats specific to this
measurement are detailed in \S\ref{sec:threats}.
