\section{Related Work}
\label{sec:related}

\biotest{} sits at the intersection of metamorphic testing
(supplying the oracle), coverage-guided greybox fuzzing (the
strongest baselines), and mutation testing (the adequacy
criterion). Our emphasis is on positioning rather than survey
recapitulation.

\subsection{Metamorphic Testing}
Metamorphic testing was introduced by~Chen et
al.~\cite{chen1998metamorphic} as a partial answer to the
oracle problem~\citep{barr2015oracle,myers1979art}. Rather than
asserting an absolute output, one asserts a metamorphic relation
constraining how outputs change under structured input
perturbations. Segura et al.~\cite{segura2016survey} survey
empirical adoption and Chen et al.~\cite{chen2018metamorphic}
catalogue the open challenges, of which MR identification is the
dominant cost in the technique's adoption.

Several lines of work attack MR identification by mining relations
from existing artefacts. MeMo~\citep{blasi2021memo} extracts MRs
from natural-language phrases in Javadoc comments, and
MR-Scout~\citep{xu2024mrscout} synthesises MRs from user-written
test cases. \biotest{} mines from a different source, the
published format \emph{specification} itself. An LLM, grounded in
the spec text via retrieval-augmented prompting and gated by a
seed-corpus validator, proposes identity-preserving transforms that
instantiate a parametric round-trip relation
($\mathit{out}(\mathit{parse}(x)) \equiv
\mathit{out}(\mathit{parse}(T(x)))$). The novelty we claim is the
combination of spec-grounded LLM-driven MR mining with a
SUT-agnostic generator and consensus oracle, not any individual
component.

\subsection{Coverage-Guided Greybox Fuzzing}
The in-process baselines we compare against typically find $2$ to
$5\times$ more bugs than blackbox baselines on a 24-hour
budget~\citep{klees2018fuzz}, an advantage B\"ohme et
al.~\cite{boehme2020boosting} explain information-theoretically.
Grammar-aware fuzzers (Zest~\citep{padhye2019zest},
Nautilus~\citep{aschermann2019nautilus},
Superion~\citep{wang2019superion}, Smart Greybox
Fuzzing~\citep{pham2021smartgreybox},
Fuzz4All~\citep{xia2024fuzz4all}) recover structural fluency but
require SUT-specific harness and build work that exceeds C2.

\subsection{Mutation Testing}
We use mutation testing as an adequacy proxy. Just et
al.~\cite{just2014mutants} establish that mutation kills correlate
with real-fault detection at $r{\approx}0.7$ on Defects4J, and
Andrews et al.~\cite{andrews2005mutation} earlier showed mutants
are an acceptable substitute for hand-seeded faults under
standard operator sets. Papadakis et
al.~\cite{papadakis2019mutation} survey the field and catalogue
the equivalent-mutant problem. We adopt Vikram et
al.~\cite{vikram2023guiding} kill-feedback corpus selection at
the pre-grading minimisation step. We complement the proxy with
the real-bug benchmark of \S\ref{sec:bug-bench}.

\subsection{Bioinformatics Pipeline and Variant-Caller Testing}
\label{sec:related-bioinformatics}

The bioinformatics community has built benchmarking infrastructure
around \emph{variant-caller correctness}. Genome in a
Bottle~\citep{zook2019giab} provides gold-standard variant calls,
and the GA4GH best-practice
protocol~\citep{krusche2019benchmarking} (\texttt{hap.py},
\texttt{vcfeval}) controls for representational equivalence
between a candidate VCF and the truth set. O'Rawe et
al.~\cite{orawe2013concordance} document substantial
inter-pipeline disagreement on the same input data. These efforts
grade the joint behaviour of caller, reference, and downstream
parsing under the assumption that VCF and SAM parsers are sound.
\biotest{} attacks the parser-correctness layer directly. A
metamorphic violation, parser disagreement, or silent record drop
that \biotest{} surfaces is a defect in a component that
GIAB-style benchmarks assume to be sound, and the two efforts are
therefore complementary.
