\section{Threats to Validity}
\label{sec:threats}

\paragraph{Construct.}
Mutation kills are an imperfect proxy for real-fault detection.
Equivalent mutants depress every tool's score equally, and we
minimise the asymmetry by reusing standard operator
sets~\citep{papadakis2019mutation}. The real-bug benchmark of
\S\ref{sec:bug-bench} grounds adequacy in real bugs as construct
triangulation.

\paragraph{Internal: bug-bench manifest is post-audit.}
The $32$-bug manifest reflects a second-pass audit that dropped
four SAM entries failing review and added three fresh htsjdk-SAM
regressions, with a strict-stringency verification policy added
after the initial freeze. Neither choice was blinded to which
bugs \biotest's paradigm could reach. We apply the post-revision
predicate uniformly to every tool to mitigate.

\paragraph{Internal: bug-detection attribution.}
The bench seed corpus follows Magma-style
PoV-seeding~\cite{hazimeh2020magma}, equalising starting
positions across all input fuzzers. Detection is verified on
tool-output triggers under a pre-fix\,/\,post-fix differential
predicate in the ground-truth fuzzing style of
Magma~\cite{hazimeh2020magma}. Canary-based
attribution from the same paper or magic-number injection per
LAVA~\cite{dolangavitt2016lava} would supersede the predicate
but require per-bug source instrumentation across all four host
languages, which we defer to future work.

\paragraph{Internal: rank-level ablation and LLM nondeterminism.}
The thirteen-rank corpus stack ships in its deployed
configuration with a single end-to-end kill rate per pair. The
only rank-level ablation reported is Ranks~12-13 on biopython/SAM.
Phase~B uses a hosted LLM whose sampling is not bit-deterministic,
and the seed-corpus MR validator is not blinded to downstream
performance. We ship the curation log with the artefact as
mitigation. The four close-margin mutation-adequacy pairs run at
$n{=}10$ and clear family-wise $\alpha{=}0.05$ under
Holm--Bonferroni. Biopython and seqan3 remain at $n{=}4$ where
samples are deterministic.

\paragraph{Internal: ablations not run.}
Iteration-count parity on seqan3/SAM would isolate the
wall-clock-vs-iteration confound behind the AFL++/libFuzzer gap.
A Ranks~1-7 vs 1-13 ablation across every pair would quantify
the augmentation-tier contribution beyond biopython/SAM. A
hand-rolled differential-only oracle would isolate the
$N{\geq}3$ majority-vote contribution.

\paragraph{External: bounded generalisation.}
The evaluation covers six $(\mathrm{SUT, format})$ pairs, two
textual formats, and four parser languages. The result does not
extend to checksum-validated binary formats (BCF, BAM, CRAM)
where structural mutations are rejected at I/O time, nor to
non-parser SUTs where the round-trip metamorphic relation does
not apply.
